Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.

The positive literal $ℓ$ must occur in
the formula from the first derivation and the
negative literal $¬ ℓ$ must occur in the formula from the second derivation,
see the pattern of \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.

>>>>

The positive literal $ℓ$ must occur in
the formula from the first derivation and the
negative literal $¬ ℓ$ must occur in the formula from the second derivation,
see the pattern of the \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.
